Here we give an upper bound (assumed loose) on the conjecture of $t$-correcting WAPB functions. More specifically, we transform the initial condition into finding $k, k+1$ such that
$$
\kraw{k}{0}{n} > \sum_{j = 1}^{\lfloor\frac{n-1}{2}\rfloor}|\kraw{k}{j}{n}|.
$$
In other words, we try to find two columns in $\KrM{n}{n}$ such that the first element is strictly greater than the sum of the absolute values of the other elements.
This means that it is impossible to find a vector $v \in \{0,\pm1\}$ such that $v\KrM{n}{k+1} = 0$.
In that sense, we loosen the condition to finding the first two consecutive columns in $\KrM{n}{n}$ such that the first element is strictly greater than $\lfloor \frac{n-1}{2} \rfloor$ times the second element.
This reformulates the condition above to
$$
\kraw{k}{0}{n} > \Big\lfloor \frac{n-1}{2} \Big\rfloor \cdot \kraw{k}{1}{n},
$$
and since $\kraw{k}{1}{n} > 0$ for all $k \leq n$, we can drop the absolute condition on each krawtchouk coefficient in the sum.

\begin{proposition}\label{prop:loose_ubound}
There is no $k$-corrector WAPB function for $k = \big\lfloor \frac{n - 1}{2}\big\rfloor$.
\end{proposition}


We can express \cref{prop:loose_ubound} as
\begin{equation*}
\begin{split}
\kraw{k}{0}{n} - \bigg\lfloor\frac{n - 1}{2}\bigg\rfloor \cdot \kraw{k}{1}{n} &> 0\\
\binom{n}{k} - \bigg\lfloor\frac{n - 1}{2}\bigg\rfloor\cdot\Bigg(\binom{n - 1}{k} - \binom{n - 1}{k - 1}\Bigg) &> 0,\\
\end{split}
\end{equation*}
for $k = \big\lfloor \frac{n - 1}{2}\big\rfloor$ and $k+1 = \big\lfloor \frac{n + 1}{2}\big\rfloor$.

\begin{proof}
    Let $k = \big\lfloor\frac{n + 1}{2}\big\rfloor$.
    \begin{itemize}
        \item If $n$ is even, $\binom{n - 1}{k} - \binom{n - 1}{k - 1} = 0$.
        \item If $n$ is odd, $\binom{n - 1}{k} - \binom{n - 1}{k - 1} \leq 0$.
    \end{itemize}

    Let $k = \big\lfloor \frac{n - 1}{2}\big\rfloor$, we can rewrite

    \begin{equation*}
        \begin{split}
            \kraw{k}{0}{n} - k \cdot \kraw{k}{1}{n} &= \binom{n}{k} - k\Bigg(\binom{n - 1}{k} - \binom{n - 1}{k - 1}\Bigg)\\
            & = \frac{n!}{(n - k)!k!} - k \Bigg(\frac{(n - 1)!}{(n - k - 1)!k!} - \frac{(n - 1)!}{(n - k)!(k - 1)!}\Bigg)\\
            & = \frac{n!}{(n - k)!k!} - k \frac{(n-1)!(n-k)!(k-1)! - (n-1)!(n-k-1)!k!}{(n-k-1)!(n-k)!(k-1)!k!}\\
            & = \frac{n!(n-k-1)!(k-1)! - k(n - 1)!(n - k)!(k - 1)! + k(n - 1)!(n - k - 1)!k!}{(n-k-1)!(n-k)!(k-1)!k!}.
        \end{split}
    \end{equation*}
    Since the denominator is strictly positive, let's focus on the sign of the numerator and let's call it $\nu$.We take out some factors of the various factorials to expose a common factor i.e.

    \begin{equation*}
        \begin{split}
            \nu &= n!(n-k-1)!(k-1)! - k(n - 1)!(n - k)!(k - 1)! + k(n - 1)!(n - k - 1)!k!\\
            & = (n-1)!(n-k-1)!(k-1)!n - (n - 1)!(n - k - 1)!(k - 1)!(n - k)k + (n - 1)!(n - k - 1)!(k-1)!k^2\\
            & = (n - 1)!(n - k - 1)!(k - 1)!\big[n - nk + 2k^2\big]
        \end{split}
    \end{equation*}

    Let $D = n - nk + 2k^2$, its sign will determine the sign of $\nu$.
    \begin{itemize}
        \item If $n$ is even, $k = \big\lfloor \frac{n - 1}{2}\big\rfloor = \frac{n}{2}$, then $D = n - \frac{n^2}{2} + 2\frac{n^2}{2} > 0, \forall n > 0$.
        \item If $n$ is odd, $k = \big\lfloor \frac{n - 1}{2}\big\rfloor = \frac{n - 1}{2}$, then $D = n - \frac{n^2 - 2n + 1}{2} - \frac{n^2 - n}{2} = n - \frac{n - 1}{2} > 0$.
    \end{itemize}

    Thus for $k = \big\lfloor \frac{n - 1}{2}\big\rfloor$ and $k+1 = \big\lfloor \frac{n + 1}{2}\big\rfloor$, it follows that $\kraw{k}{0}{n} - k\cdot \kraw{k}{1}{n} > 0$ as well as $\kraw{k+1}{0}{n} - (k+1)\cdot \kraw{k+1}{1}{n} > 0$, meaning there are no $k$-corrector WAPB.
\end{proof}
